%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {Samsung R\&D Institute} % Organization
    {Bangalore, India} % Location
    {Sep. 2018 - PRESENT} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Currently working with the Camera Systems team for the bring-up and development support of cameras in new mobile devices.}
      \item {Owned the development of camera for new models at the HAL (Hardware Abstraction Layer) and the Kernel layers.}
      \item {Developed various scripts to automate daily tasks such as KPI collection and aggregation, as well as other internal processes. }
      \item {Worked with a multicultural team with members from India, South Korea, Vietnam and China.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer Intern} % Job title
    {Zynga} % Organization
    {Bangalore, India} % Location
    {Jan. 2018 - Jun. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Helped create a microservice that enabled the organisation to be GDPR compliant.}
      \item {Wrote scalable web APIs in Go and unit-tests, regression tests for the system}
      \item {Found and suggested key points where the system can be optimized and the development overhead can be reduced}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer Intern} % Job title
    {Samsung R\&D Institute} % Organization
    {Bangalore, India} % Location
    {Mar. 2017 - Jul. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Worked on the creation of a packet generation tool for the Data Link Layer of 5G network }
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer Intern } % Job title
    {Vasudhaika Software Private Limited} % Organization
    {Hyderabad, India} % Location
    {May. 2016 - Jul. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Worked on a classifier that picks websites of relevance using an ensemble of classifiers like SVM. Achieved 87\% accuracy}
      \item {Helped in providing an alternative to manual segregation of websites, thus reducing the workload of an entire department}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
