%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Extracurricular Activity}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Member} % Affiliation/role
    {Toastmasters International} % Organization/group
    {Bangalore, India} % Location
    {Feb. 2018 - PRESENT} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
      \item {Currently on Level 2 on the "Presentation Mastery" path under pathways.}
      \item {Have performed speeches at multiple branches including Bangalore, Delhi and Seoul.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Core Member} % Affiliation/role
    {Department of Publications and Correspondence} % Organization/group
    {Pilani, India} % Location
    {Jan. 2015 - Dec. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
      \item {Department of PCr works towards bringing participation and increasing footfall for the college fests at BITS Pilani from colleges all over India.}
      \item {Mentored a two tier team of 25 students to publicize events and communicate with 500+ colleges and 4000+ students.}
      \end{cvitems}
    }

%---------------------------------------------------------
    %*************** Need to decide whether this is worth it
  \cventry
    {Tutor} % Affiliation/role
    {Software Competency Exam, Samsung R\&D Institute} % Organization/group
    {Bangalore, India} % Location
    {Oct. 2018 - PRESENT} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
      \item {Helped prepare engineers for the internal software competency test that tests for data structures, algorithms and problem solving capability.}
      \item {Cleared the exam myself in the first attempt. Currently only 15\% of the engineers in the company have been able to pass the exam.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
